---
title: "Block4: sample statistics"
output: github_document
---

```{r}
library(tidyverse)
library(here)
library(e1071)
library(skimr)
library(lubridate)
library(forcats)
library(ggplot2)
library(infer)
sales <- readRDS(here::here("data/sales.rds"))

mu <- sales %>%
  summarize(stat = mean(resale_price))
mu
```

```{r}
sales %>%
  sample_n(100) %>%
  summarize(stat = mean(resale_price))
```
```{r}
sample_mean <- function(data, size = 500) {
  data %>%
    sample_n(size) %>%
    summarize(stat = mean(resale_price))
}

sampled_means <- rerun(500, sample_mean(sales)) %>% bind_rows()

sampled_means %>%
  ggplot(aes(x = stat)) +
  geom_histogram() +
  geom_vline(xintercept = mu$stat)
```

```{r}
# sample of 500 (from the entire database)
sales_sample <- sales %>%
  sample_n(500)

# mean of the sample
x_bar <- sales_sample %>%
  summarize(stat = mean(resale_price))
x_bar

# same with different library
sales_sample %>%
  specify(response = resale_price) %>%
  calculate(stat = "mean")
```

```{r}
# Bootstrapping
bootstrapped_resale_price <- sales_sample %>%
  specify(response = resale_price) %>%
  generate(reps = 500) %>%
  calculate(stat = "mean")

bootstrapped_resale_price %>%
  visualise() +
  geom_vline(xintercept = x_bar$stat)
```

```{r}
bootstrapped_resale_price %>%
  get_ci()
```
### Exercise 1: Using RStudio’s help panel, find out how to use the standard error method with get_ci. Do you find the same values?
```{r}

```


### Exercise 2: Try changing the value of your confidence level (by default, get_ci uses 0.95). What do you observe as you ask for higher confidence levels?
```{r}

```


### Exercise 3: Repeat the previous steps using a different value for n, the size of our original sample. What does the new confidence interval compare to the previous one?
```{r}

```

```{r}
# Confidence intervals for subsets:
# x_bar_mp_all <- sales %>%
#  filter(town == "MARINE PARADE") %>%
#  summarize(stat = mean(resale_price))

# x_bar_mp
```
```{r}

sales %>%
  # filter(floor_area_sqm == 67) %>%
  filter(town == "MARINE PARADE") %>%
  View()


# sample of 500 (from the entire database)
sales_sample_mp <- sales %>%
  filter(town == "MARINE PARADE") %>%
  sample_n(100) # Error: `size` must be less or equal than 485 (size of data), set `replace` = TRUE to use sampling with replacement.

# mean of the sample
x_bar_mp <- sales_sample_mp %>%
  summarize(stat = mean(resale_price))
x_bar_mp



bootstrapped_resale_price_mp <- sales_sample_mp %>%
  filter(town == "MARINE PARADE") %>%
  specify(response = resale_price) %>%
  generate(reps = 500) %>%
  calculate(stat = "mean")

bootstrapped_resale_price_mp %>%
  visualise() +
  geom_vline(xintercept = x_bar$stat)

bootstrapped_resale_price_mp %>%
  get_ci()
```

```{r}
# 4.4 Comparing means between groups

town_means <- sales %>%
  filter(town == "QUEENSTOWN" | town == "MARINE PARADE") %>%
  group_by(town) %>%
  summarise(mean = mean(resale_price))
town_means
```

```{r}
ggplot() +
  geom_histogram(
    data = sales %>%
      filter(town == "QUEENSTOWN" | town == "MARINE PARADE"),
    mapping = aes(x = resale_price, y = ..density.., group = town, fill = town),
    position = position_dodge()
  ) +
  geom_vline(
    data = town_means,
    mapping = aes(xintercept = mean, group = town, color = town)
  )
```

```{r}
bootstrapped_resale_price_qt <- sales %>%
  filter(town == "QUEENSTOWN") %>%
  specify(response = resale_price) %>%
  generate(reps = 100) %>%
  calculate(stat = "mean")

bootstrapped_resale_price_qt %>%
  get_ci()
```
```{r}
# test the significance of the difference more formally with infer

mean_diff <- sales %>%
  filter(town == "MARINE PARADE" | town == "QUEENSTOWN") %>%
  specify(formula = resale_price ~ town) %>%
  calculate(stat = "diff in means", order = c("QUEENSTOWN", "MARINE PARADE"))
mean_diff
```

```{r}
# We then generate a set of sampled datasets. But instead of doing a simple bootstrap, we generate each sample based on the null hypothesis, namely that there is no difference between the mean of the two towns.

null_distribution <- sales %>%
  filter(town == "MARINE PARADE" | town == "QUEENSTOWN") %>%
  specify(formula = resale_price ~ town) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 500, type = "permute") %>%
  calculate(stat = "diff in means", order = c("QUEENSTOWN", "MARINE PARADE"))

null_distribution %>%
  visualise(bins = 100) +
  shade_p_value(obs_stat = mean_diff, direction = "greater")
```

```{r}
null_distribution %>%
  get_pvalue(obs_stat = mean_diff, direction = "greater")
```

```{r}
sales %>%
  filter(town == "MARINE PARADE" | town == "QUEENSTOWN") %>%
  specify(formula = resale_price ~ town) %>%
  # hypothesize(null = "independence") %>% # disable the null hypothesis
  generate(reps = 500, type = "bootstrap") %>% # set type to bootstrap
  calculate(stat = "diff in means", order = c("QUEENSTOWN", "MARINE PARADE")) %>%
  get_ci()
```

### Exercise 4: In the RStudio help, find out what the direction argument does for the get_p_value and shade_p_value functions. Try setting it to both on the data above.
```{r}

```



### Exercise 5: Are the resale prices means between Marine Parade and Bukit Timah significantly different?
```{r}

```


### Exercise 6: During the previous week, we saw that the price of a flat can be quite different depending on what storey the flat is located on. Use the same procedure to see if the average price of 3 room flats on storey 04-06 is significantly different from 3 room flats on storey 07-09.
```{r}

```
