---
title: "Mini-assignment#1"
output: github_document
---
## Use tidyverse staples "filter", "arrange", "group_by", and "summarize".
```{r}

library(tidyverse)
library(here)

sales <- readRDS(here::here("data/sales.rds"))
```
"1. What is the earlier lease commencement date and where are these flats located?"
```{r}
ans1 <- sales %>%
  filter(lease_commence_date == min(sales$lease_commence_date)) %>%
  group_by(town) %>%
  summarise_at(vars(lease_commence_date), funs(mean(., na.rm = TRUE))) %>%
  select(matches("town") | matches("lease_commence_date"))
toString(ans1)
```
"2. What are the largest HDB flats in Singapore? How much did they sell for?"
```{r}
ans2 <- sales %>%
  filter(floor_area_sqm == max(sales$floor_area_sqm)) %>%
  select(matches("town") | matches("resale_price"))
toString(ans2)
```
"3. What is the most expensive flat in Punggol?"
```{r}
ans3 <- sales %>%
  filter(town == "PUNGGOL") %>%
  summarize(stat = max(resale_price))
toString(ans3)

# to verify:
ans3_chk <- sales %>%
  filter(town == "PUNGGOL") %>%
  arrange(-resale_price)
# %>% View()
```
"4. Which town has, on average, the largest flats (by floor area)?"
```{r}
ans4 <- sales %>%
  group_by(town) %>%
  summarise_at(vars(floor_area_sqm), funs(mean(., na.rm = TRUE))) %>%
  filter(floor_area_sqm == sales %>%
    group_by(town) %>%
    summarise_at(vars(floor_area_sqm), funs(mean(., na.rm = TRUE))) %>%
    select(matches("floor_area_sqm")) %>%
    max()) %>%
  select(matches("town") | matches("floor_area_sqm"))
toString(ans4)
```
"5. Which town has, on average, the cheapest flats per square meter?"
```{r}
sales <- transform(sales, price_per_sqm = resale_price / floor_area_sqm)
ans5 <- sales %>%
  group_by(town) %>%
  summarise_at(vars(price_per_sqm), funs(mean(., na.rm = TRUE))) %>%
  filter(price_per_sqm == sales %>%
    group_by(town) %>%
    summarise_at(vars(price_per_sqm), funs(mean(., na.rm = TRUE))) %>%
    select(matches("price_per_sqm")) %>%
    min()) %>%
  select(matches("town") | matches("price_per_sqm"))
toString(ans5)
```
