---
title: "Block3_assignment1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```
```{r}
library(tidyverse)
library(here)
library(e1071)
library(skimr)
library(lubridate)
library(forcats)
library(ggplot2)
sales <- readRDS(here::here("data/sales.rds"))
```


## Exploration of all variables in the dataset

1. Summarize the different continuous variables (area, price, remaining lease) as well as the nominal/ordinal variables (month, flat_type, town, flat_model, storey_range), summarize these variables in both table (stats on central tendency and distribution) and visual form.
```{r}
floor_area_sqm <- sales$floor_area_sqm
resale_price <- sales$resale_price
remaining_lease <- sales$remaining_lease
var_list_cont = list("floor_area_sqm", "resale_price", "remaining_lease")

month <- sales$month
town <- sales$town
flat_type <- sales$flat_type
flat_model <- sales$flat_model
storey_range <- sales$storey_range
var_list_other = list("month","town","flat_type","flat_model","storey_range")

"Central tendency (only numeric data):"
manual_mode <- function(x, na.rm = FALSE) { # we don't use 'mode' as a function name because it already exists
  if (na.rm) {
    x <- x[!is.na(x)]
  }
  ux <- unique(x)
  return(ux[which.max(tabulate(match(x, ux)))])
}

for (variable in var_list_cont){
  print(variable)
  a<- get(variable)
  print(  paste("Mode: ", toString(manual_mode(a)),", Mean: ", toString(mean(a)), ", Median: ", toString(median(a)) )   )
}

"Dispertion (all data types):"
for (variable in var_list_cont) {
  print(variable)
  a<- get(variable)
  print ( skim(a) )
}
for (variable in var_list_other) {
  print(variable)
  a<- get(variable)
  print ( skim(a) )
}
```
```{r}
"Visualization (only numerical data)"
for (variable in var_list_cont) {
  print(variable)
  a<- get(variable)
  
  print( ggplot(sales, aes(x = a)) + 
    geom_histogram(aes(y = ..density..)) + #, binwidth = 5
    stat_function(fun = dnorm, args = list(mean = mean(a), sd = sd(a)))  )
  
  print( ggplot(sales, aes(x = 1, y = a)) + 
    geom_boxplot() )
  
  print( ggplot(sales, aes(x = 1, y = a)) + 
  geom_violin() )
}

```

2. Analyze the distribution of (some of) these variables for different subsets of the data. For example, explore the difference between towns, or between flat types.

```{r}
for (variable in var_list_cont) {
  print(variable)
  a<- get(variable)
  
  print( ggplot(sales, aes(x = a)) + 
    geom_histogram() + #binwidth = 10
    facet_wrap(vars(town), scales = "free_y") )
  
  print( ggplot(sales, aes(x = a)) + 
    geom_histogram() + #binwidth = 10
    facet_wrap(vars(flat_type), scales = "free_y") )
  
  print( ggplot(sales, aes(x = flat_type, y = a)) + 
  geom_violin() )
  
  p<- ggplot(sales, aes(x = town, y = a)) + 
    geom_boxplot() 
  print( p + theme(axis.text.x = element_text(angle = 90)) )
}
```
3. Analyze the distribution of at least one variable for unique combinations of town and flat_type (for each town, for each flat type: Ang Mo Kio, 1 room; Ang Mo Kio 2 room; etc.)
```{r}
for (t in unique(town)) {
  print(t)
  print( ggplot(sales %>% filter(town == t), aes(x = flat_type, y = resale_price)) + 
    geom_violin() )
}
for (f in unique(flat_type)) {
  print(f)
  p<-  ggplot(sales %>% filter(flat_type == f), aes(x = town, y = resale_price)) + 
    geom_violin() 
  print( p + theme(axis.text.x = element_text(angle = 90)) )
}
```
4. Analyze change in resale price per square meter over time. Use a 6-month moving average to do so.
```{r}
library(lubridate)
mon <- month(as.Date(sales$month))*(year(as.Date(sales$month)) -year(as.Date(min(sales$month))) )
sales <- transform(sales, price_per_sqm = resale_price / floor_area_sqm, mont = mon)

month_list <- seq(min(mon), max(mon), by=6)
print(month_list)

for (i in month_list){
  range <- seq(i,i+6)
  new_col <- ifelse(sales$mont %in% range, i, -1)
  
  sales <- transform(sales, mont = ifelse(new_col==-1,mont, i)) 
  print(paste ("New 6-months period starting from: ", toString(i))  )

}
sales <- sales %>% mutate( mont = as_factor(mont) )
print( ggplot(sales, aes(x = mont, y = price_per_sqm)) + 
  geom_violin() )
print( ggplot(sales, aes(x = price_per_sqm)) + 
  geom_histogram() + #binwidth = 10
  facet_wrap(vars(mont), scales = "free_y") )
```

